Hierarchical time series forecasting in Emergency Medical Services

### 2022-11-16 manuscript/03-experiment.qmd
add new references and typos
typo

**Poisson Regression using tscount:** We consider another Poisson regression model that takes into account serial dependence in addition to covariates used in the GLM model. To that end, we use `tsglm()` function in _tscount_ package in R to model the attended incidents. The logarithmic link function is used to ensure that the parameter of Poisson distribution is always positive. This model can be estimated via maximization of the likelihood function based on Poisson mass function. The regression model captures the short range serial dependence by including the three order autoregressive terms.

>>>>

**Poisson Regression using tscount: ** We consider another Poisson regression model that takes into account serial dependence in addition to covariates used in the GLM model. To that end, we use `tsglm()` function in _tscount_ package in R [@JSSv082i05] to model the attended incidents. The logarithmic link function is used to ensure that the parameter of Poisson distribution is always positive. This model can be estimated via maximization of the likelihood function based on Poisson mass function. The regression model captures the short range serial dependence by including the three order autoregressive terms.
